%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%



%-------------------------------------------------------------------------------

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts]

% \definecolor{lighttext}{HTML}{CA63A8}

% Set false if you don't want to highlight section with awesome color

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


\colorlet{awesome}{awesome-red}

% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
% Colors for text
% Uncomment if you would like to specify your own color
\definecolor{darktext}{HTML}{000000}
\definecolor{text}{HTML}{000000}
\definecolor{graytext}{HTML}{000000}
\definecolor{lighttext}{HTML}{000000}


\setbool{acvSectionColorHighlight}{true}






%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
%\photo{2020-01-18.jpg}
\name{Ismail}{EZZAKI}
\position{Master Student{\enskip\cdotp\enskip}Freelancer Programmer}
\address{812 Ait kdif Ouarzazate Morocco}

\mobile{(+212) 708070221}
\email{ismail.ezzaki@edu.uca.ma}
\homepage{ismailezzaki.me}
\github{ismailezzaki96}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra informations}

\quote{``be the change you want to see in the world"}

%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
{Company Recruitment Team}
{Google Inc.\\1600 Amphitheatre Parkway\\Mountain View, CA 94043}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Letter of Motivation
}
% How the letter is closed
 
% Any enclosures with the letter
\letterenclosure[Attached]{Curriculum Vitae}





%TODO Dear members of Selection Committee,
\letteropening{ Dear members of Selection Committee,  
}
% Title
\newcommand{\thesis}{  Experimental Heavy-Ion Physics 
}
%-------------------------------------------------------------------------------
\begin{document}
	
	% Print the header with above personal informations
	% Give optional argument to change alignment(C: center, L: left, R: right)
	%\makecvheader[C]
	
	% Print the footer with 3 arguments(<left>, <center>, <right>)
	% Leave any of these blank if they are not needed
	
	% Print the title with above letter informations
	


	
	
	
	%-------------------------------------------------------------------------------
	%	LETTER CONTENT
	%-------------------------------------------------------------------------------
	\begin{cvletter}
		
				\makelettertitle
My name is Ismail EZZAKI, I am 25 years old, I came across your recent advertisement on your Facebook page for the position of Language and Cross-Culture Facilitator. I believe my achievements and skills rightly match your requirements. As requested, I have enclosed my resume that will give you detailed information about my work history and educational background.

You will note from my enclosed CV that I have many of the attributes that you are seeking for this position. Please consider the following:

education and activities :
My education includes a master’s degree  in physics (2 in my promotion), during my university studies I participate in many activities :
I had the opportunity to teach undergraduate students  
I participated in the Enactus club for 2 years  when I was part  of a team of 50 students we create social entropranial projects 
and I have also taken courses on soft skills
I volunteered for two months in the Mohammed IV disability association when we helped children with Intellectual Disabilities to learn how to do simple tasks with the computer: write office documents, use Google search engine … 

Fluency in English:  as I mentioned in my cv, my level in English is C1 which is equal to 95 on the TOEFL test 

Intercultural awareness: I participate in many international summer schools in physics, and I can communicate perfectly with people with foreign languages from different backgrounds, nationalities, and religions.

Excellent communication skills in English and Arabic: Arabic is my mother tongue so i can say with confidence that i have Excellent communication skills in both: English and Arabic 

Good listening skills: When I was working on projects in the Enactus club with teammates, I always tried to take the active listening role and take notes on the details of the project. Ask questions to hear my colleagues' ideas. This helps me develop my communication and ability to hear everyone's side of a situation

Strong organizational and coordination skills: I can finish work before a deadline and turn it in on time. I keep my desk organized with a paper-filing system I created in college, also I use the Notion app that helped me to multitask and prioritize work tasks and increased my productivity.

Ability to act with diplomacy: During my voluntary work, I learned how to negotiate and how to speak to local authorities especially “lmekedem” and where and how to get the authorization to work in the field, also I learned from my soft skills course how to resolve conflict and find a common ground between people 

Ability to work independently and as part of a team: Although I work well independently for example due to the lockdown I did my master thesis independently, also I am equally comfortable working as a part of a team, for example, I joined the  Enactus club for 2 years and I worked perfectly with more than 50 members.

Good computer skills: I have 4 years of experience working as a freelance web and mobile developer so I am familiar with most of the computer’s skills: fast typing, Advanced skills in Microsoft office, programming… 

Moroccan citizenship: I have Moroccan citizenship and You can download a scanned version of my identity card here

My previous voluntary experience in addition to my passion for effective communication, professionalism, and hard work make me a strong candidate for this position. Should you have any questions, please feel free to contact me. Thank you for your time and consideration.

Sincerely,

\vspace{2ex}
Sincerely thank you for consideration.\\
Respectfully yours,\\
Ismail EZZAKI
	\end{cvletter}
	
	
	%-------------------------------------------------------------------------------
	% Print the signature and enclosures with above letter informations

	
\end{document}
